Placeholder Title... Something About Delegating Quantum Computations

### 2019-09-07 paper.tex
start local Hamiltonian construction

We then attempt to construct a 2-local Hamiltonian with ground state $$\phi=\sum_{t=0}^TU_t...U_1\ket{x}\otimes\ket{\hat{t}}$$. We do so by ensuring states perpendicular to it have high eigenvalues.

>>>>

We then attempt to construct a 2-local Hamiltonian with ground state: $$\phi=\sum_{t=0}^TU_t...U_1\ket{x}\otimes\ket{\hat{t}}$$
We do so by ensuring states perpendicular to it have high eigenvalues. The basic construction comes from \cite{kitaev2002classical}. The simplification comes from \cite{biomonte_love_2008}.
